# Jooyoung Yu 

---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## 1. Reading Data set

Read csv files.

```{r, echo=TRUE}
unzip(zipfile = "activity.zip", exdir = ".")

dat<-read.csv("activity.csv")
summary(dat)

```

## 2. Histogram of the total number of steps taken each day


```{r, echo=TRUE}
dat_perday <- aggregate(steps ~ date, data = dat, sum, na.rm = TRUE)
hist(dat_perday$steps)

dat_perday_mean <- round(mean(dat_perday$steps),2)
dat_perday_median <- round(median(dat_perday$steps),2)

```

## 3. Mean and median number of stemps taken each day
```{r, echo=TRUE}
dat_perday_mean <- round(mean(dat_perday$steps),2)
dat_perday_median <- round(median(dat_perday$steps),2)
```
* mean of daily steps : `r dat_perday_mean`
* median of dail steps : `r dat_perday_median` 


## 4. Time series plot of the average number of steps taken
```{r, echo=TRUE}
dat_perinterval <- aggregate(steps ~ interval, data = dat, mean, na.rm = TRUE) 
plot(dat_perinterval$interval, dat_perinterval$steps, xlab="interval", ylab = "steps", main="Average daily activity pattern",type = "l")
```


## 5. The 5-minute interval that, on average, contains the maximum number of steps
```{r, echo=TRUE}
max_steps <- dat_perinterval[which.max(dat_perinterval$steps),1]
print(max_steps)
```

## 6. Code to describe and show a strategy for imputing missing data
To fill the missing data, mean of steps grouped by 5-minutes interval are set.
```{r, echo=TRUE}
library(dplyr)
dat_filled <- dat %>% group_by(interval) %>% mutate(steps = ifelse(is.na(steps), mean(steps, na.rm=TRUE), steps))
dat_filled <- as.data.frame.data.frame(dat_filled)

```


## 7. Histogram of the total number of steps taken each day after missing values are imputed
```{r, echo=TRUE}
dat_perday2 <- aggregate(steps ~ date, data = dat_filled, sum, na.rm = TRUE)
hist(dat_perday2$steps, ylim=c(0,40))
```


```{r}
dat_perday_mean2 <- mean(dat_perday2$steps)
dat_perday_median2 <- median(dat_perday2$steps)
```

* mean of daily steps : `r dat_perday_mean2`
* median of dail steps : `r dat_perday_median2`
>>> After imputing missing data, mean there median value is little increased.

## 8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
wday <- weekdays(as.Date(dat_filled$date))
dat_filled <- cbind(dat_filled, wday)
dat_filled <- dat_filled %>% mutate(isweeked = ifelse(wday == "토요일" | wday == "일요일", TRUE, FALSE))

dat_weekday <- dat_filled[!dat_filled$isweeked,]
dat_weekend <- dat_filled[dat_filled$isweeked,]

par(mfrow=c(2,1))
dat_weekday_perinterval <- aggregate(steps ~ interval, data = dat_weekday, mean, na.rm = TRUE) 
plot(dat_weekday_perinterval$interval, dat_weekday_perinterval$steps, xlab="interval", ylab = "steps", main="weekday pattern",type = "l")

dat_weekend_perinterval <- aggregate(steps ~ interval, data = dat_weekend, mean, na.rm = TRUE) 
plot(dat_weekend_perinterval$interval, dat_weekend_perinterval$steps, xlab="interval", ylab = "steps", main="weekend pattern",type = "l")
```



